\section{Optimization of measurement parameters}

Optimal measurement conditions are one of the requirements for high quality
scientific results. There are many adjustable parameters which can influence
quality of the measurement and their optimal values highly depend on the
samples under measurement. Further analysis is focused on optimization of
measurement parameters of nucleic acids using 244 and 257-nm excitation
wavelengths. PolyU was chosen as the sample for these experiments because
uracil is known to be the most susceptible base for photodecomposition and our
further experiments were conducted on olygo and polynucleotides and thus polyU
is better model molecule than for example mononucleotide UMP. The main
parameters which needed to be determined were excitation laser power, length of
accumulation, sample volume and concentration. Moreover, the optimal sample
rotation speed needed to be found for the experiments using spinning cell.

\input{results_and_discussion/power_optimization}
\input{results_and_discussion/concentration_optimization}

\subsection{Volume optimization}
From DNA hairpins optimization.

\input{results_and_discussion/length_of_accumulation}
\input{results_and_discussion/rotation_optimization}


\subsection{Low volumes artefact}
When the measurement is performed in backscattering geometry from spinning cell
with low volume the spectrum contains also a spectrum of air which is dominated
by bands of \ch{O2} at 1556\,\icm{} and \ch{N2} at 2331\,\icm{} with clearly
clearly distinguished rotation bands. (The spectrum can be taken from the
measurements of algae 15N or UV SERS on Rh.)
