\section{Design of UV Raman experiment}

Work on the construction of a new UV Raman spectrometer was an incremental
process. It was necessary to consider the equipment already present in the lab,
mainly the laser system, CCD camera and optical table and specify parameters of
chosen commercial spectrograph. Then the first functional prototype was
constructed and improved for measurement of polarized UV Raman spectra. The
first calibration wavenumber calibration technique of measured Raman spectra
was adopted based on the literature. Then we started to deal with
photo-decomposition of samples by designing a spinning cell which could contain
as small as cca. 20 \g{m}l volumes of samples. After that we widened the range
of usable excitation wavelengths of the instrument and decided to seek for a
new means of wavenumber calibration and after some research and trials and
errors we settled with calibration to the spectra of Pt lamp. And then, the
aparatus was enhanced to enable temperature measurements in backscattering
geometry. Next sections describe each step of the development of the UV Raman
spectrometer in more details.


\subsection{Selection of spectrograph parameters}
\begin{docitemize}
	\item Introduce dispersion according to focal length and groove density of
	grating.
	\item Produce table of possible scenarios.
	\item Present decision criteria.
\end{docitemize}


\subsection{Initial layout of the instrument}
\begin{docitemize}
	\item Draw a schema
	\item Briefly describe used optical elements
\end{docitemize}


\input{results_and_discussion/focusing_lens_estimation}


\subsection{Wavenumber calibration to organic solvents}
\begin{docitemize}
	\item Overview possibilities
	\item Describe why cyclohexane and deuterated cyclohexane
	\item Describe created calibration program
\end{docitemize}


\subsection{Polarized Raman measurements}
\begin{docitemize}
	\item Describe tested elements
	\item Describe polarizers evaluation
\end{docitemize}


\subsection{Design of the spinning cell}
\begin{docitemize}
	\item Overview possible solutions
	\item Draw a schema
	\item Describe the used cell
	\item Describe the method of calibration of the dependence of the rotation
	speed on the input voltage
\end{docitemize}


\subsection{Redesign for multiple excitation wavelengths}
\begin{docitemize}
	\item Draw a new spectrometer schema
	\item Describe briefly newly used elements
\end{docitemize}


\subsection{Better wavenumber calibration}
\begin{docitemize}
	\item Describe the advantages and disadvantages of using organic solvents
	\item Describe the possibility of use Hg lamp
	\item Describe the advantages of Pt lamp
	\item Describe parameters of the new Pt lamp
	\item Present spectrum of Pt lamp
	\item Show new schema of the apparatus
\end{docitemize}


\subsection{Redesign of the spectrometer for backscattering}
\begin{docitemize}
	\item Present new schema
	\item Briefly describe new optics
	\item Present schema of mirror holder right in front of Cassegrain
\end{docitemize}


\subsection{Construction of the thermostated sample holder}
\begin{docitemize}
	\item Draw the technical drawing
	\item Present the used elements
	\item Overview the performance
\end{docitemize}
