\textcite{Myers1988} calibrated wavenumbers using cyclohexane in
combination with various \ch{H2} Raman-shifted laser lines and mercury
emission lines. \textcite{Su1990} calibrated Raman spectra in frequency with
ethanol. \textcite{Toyama1991, Toyama1996} used for wavenumber calibration
the Raman bands of ethyl acetate/dioxane (2:1 v/v), which had been measured
with visible-laser excitation on a spectrometer calibrated with indene Raman
bands and neon emission lines. \textcite{Kaminaka1992} calibrated Raman
shifts with cyclohexane and acetone as the secondary standard, while their
Raman bands were calibrated with indene, with the use of visible excitation.
\textcite{Benson1992} calibrated the wavenumber shift with the use of the
Raman spectra of acetonitrile and acetone. \textcite{Benson1993} used carbon
tetrachloride for wavenumber shift calibration standard.
\textcite{Hashimoto1993} made wavenumber calibration with the Raman bands of
cyclohexanone/acetonitrile (1:1 v/v). \textcite{Mukerji1995} calibrated spectra
against neat solution of ethanol and \textit{n}-penthane.
\textcite{Russell1995} performed wavenumber calibration in UV-laser excited
Raman spectra using the well known Raman lines of dioxane, carbon
tetrachloride, and acetonitrile. \textcite{Gustafson1988} calibrated
wavenumber shift using the Raman spectrum of acetonitrile.
\textcite{Leonard1994} calibrated wavenumber shift with the use of the Raman
spectrum of cyclohexane. \textcite{Takeuchi1990} made wavenumber calibration
by using the Raman bands of cyclohexanone/acetonitrile (1:1, v/v), the
wavenumber of which had been established with visible-laser excitation on a
spectrometer calibrated with indene Raman bands and neon emission lines.
\textcite{Takeuchi1995} calibrated wavenumber axis of the spectra by using
the spectrum of a mixture solution of ethyl acetate/dioxane (2:1 v/v) as a
wavenumber standard. \textcite{Tuma1995} performed wavenumber
calibration in UVRR spectra using well-known Raman lines of dioxane, carbon
tetrachloride, and acetonitrile. \textcite{Wen1997} calibrated Raman
frequencies using a standard liquid mixture of carbon tetrachloride and
acetonitrile. \textcite{Fujimoto1998} made wavenumber calibration of the
spectra by use of the Raman bands of a 2:1 (v/v) mixture of ethyl
acetate/1,4-dioxane (257\,nm excitation) or of a 1:1 (v/v) mixture of
cyclohexanone/acetonitrile (213\,nm). \textcite{Mukerji1998} calibrated data
with acetone, ethanol, and pentane. \textcite{Wen1998} used \ch{Na2SO4} as
internal frequency (981\,\icm) standard, and Raman frequencies were
calibrated to $\pm1 $\,\icm{} using \ch{ccl4}/\ch{CH3CN} mixture.
\textcite{Suen1999} calibrated against neat solutions of ethanol and acetone,
for which the Raman band frequencies were known. \textcite{Toyama1999}
performed wavenumber calibraion by use of the Raman bands of
ethylacetate--dioxane (2:1, v/v). \textcite{Wen1999} calibrated Raman
frequencies by using a standarad liquid mixture of carbon tetrachloride and
acetonitrile. \textcite{Sokolov2000} calibrated data with acetone, ethanol and
pentane. \textcite{Toyama2001} made wavenumber calibration of Raman spectra
by using the Raman spectrum of a 2:1 (v/v) mixture of ethylacetate/1,4-dioxane.
\textcite{Fujimoto2002} calibrated Raman spectrometer by using the Raman bands
of a 2:1 (v/v) mixture of ethylacetate and dioxane for 257-nm excitation or a
1:1 (v/v) mixture of cyclohexanone and acetonitrile for 229-nm excitation.
\textcite{Toyama2002} performed wavenumber calibration of Raman spectra by use
of the Raman bands of a 2:1 (v/v) mixture of ethyl acetate and 1,4-dioxane.
\textcite{Nelson2004} calibrated the Raman shift axis with pure ethanol.
\textcite{Toyama2005,Toyama2005a} made wavenumber calibration of Raman spectra
by use of Raman bands of a 2:1 (v/v) mixture of ethyl acetate and 1,4-dioxane.
\textcite{Billinghurst2006,Billinghurst2006a} perforemd frequency calibration
by measuring the Raman scattering of organic solvents for whom the peak
positions are known (\textit{n}-pentane, cyclehexane, dimethylformamide,
ethanol, acetonitrile, and acetic acid). \textcite{Jirasek2006} wavenumber
calibrated abscissa of each acquired spectrum using an ethanol spectrum as the
calibration standard. \textcite{Kundu2007} performed frequency calibration by
measuring the resonance Raman spectra of organic solvents whose peak positions
were known (acetonitrile, dimethylformamide, \textit{n}-hexane,
\textit{n}-pentane, cyclohexane and acetic acid). \textcite{Yarasi2007}
performed frequency calibration by measuring Raman scattering of solvents of
known frequencies (acetonitrile, dimethylformamide, carbon tetrachloride,
ethanol, and pentane). \textcite{Knee2008} calibrated spectra against ethanol,
acetone and pentane. \textcite{Billinghurst2009} performed calibration by
measuring the Raman scattering of solvents for which the peak positions are
known (\textit{n}-pentane, cyclohexane, \textit{N,N}-dimethilformamide,
ethanol, acetonitrile, and acetic acid). \textcite{Jayanth2009} calibrated
spectra using known solvent bands (dimethyl formamide, acetonitrile,
trichloroethylene, isopropanol, indene, and cyclohexane). \textcite{Shaw2009}
used a spectrum of ethanol to calibrate the abscissa of each spectrum.
\textcite{Jayanth2011} carried out calibration using spectra of standard
solvents: dimethyl formamide, acetonitrile, trichloroethylene, isopropanol,
indene, and cyclohexane. \textcite{Oladepo2011} performed frequency calibration
by measuring the Raman scattering of solvents for which the peak positions were
known (cyclohexane, \textit{N,N}-dimethylformamide, methanol, acetonitrile,
dimethyl sylfoxide and acetic acid). \textcite{Billinghurst2012} performed
frequency calibration by measuring the Raman scattering of organic solvents for
which the peak positions are known (\textit{n}-pentane, cyclohexane,
dimethylformamide, ethanol, acetonitrile and acetic acid).
\textcite{Kumamoto2012} calibrated grating dispersion with the laser line
(0\,\icm), and Raman bands of boron nitride (1370\,\icm) and acetonitrile
(2249\,\icm). \textcite{Srivastava2008,Muntean2013} used Raman spectra of
dimethylsulfoxide as a standard for wavenumber calibration.
\textcite{Mondal2016} calibrated the recorded spectra using known bands of
standard solvents, e.g. acetonitrile, isopropanol, cyclohexane and dimethyl
formamide.
