\chapter{UV RRS measurements of nucleic acids}

Despite the decades of intensive research, \emph{nucleic acids} (NA) represent
still a permanent object of the structural studies, which focus on
characterizing NA local geometric arrangement, its formation and collapse
depending on the internal (nucleobase sequence) and external (environmental
conditions, intermolecular interactions) parameters.
The reason is the rich structural polymorphism of nucleic acids, which are in
addition to the classic Watson-Crick duplex capable to adopt a variety of
non-canonical structures, such as hairpins, cruciforms, triplexes, quadruplexes
or i-motifs.
It has been also shown that the processes of the expression of genetic
information, of its modification and transfer are controlled through specific
nucleic acid-protein interactions.
However, detailed molecular mechanisms of these key biological processes are
often unknown
\parencite{%
	Bansal2014,%
	Kaushik2016,%
	Yamamoto2021%
}

A variety of experimental techniques has been used to investigate the
structural arrangement of nucleic acids in their natural environment.
Many of them were gradually developed to achieve credible and
well-interpretable results.
One of the relatively new techniques that was considered as perspective is the
resonance Raman scattering excited in the ultraviolet spectral region (UV RRS).
UV RRS of NA and their components have been measured since the beginning of
seventies.
In contrast to the original optimistic expectations, this method is though
currently applied in nucleic acid studies only rarely.

This chapter represents a brief overview of the published studies, summarizes
the main assets to NA research and tries to draw attention to possible
pitfalls.
In addition to the results achieved, great attention is paid to the used
apparatus and the methodology of the experiment, data treatment and
interpretation.


\input{introduction/uvrr_na_experiment}
\input{introduction/uvrr_na_studies}
\input{introduction/uvrr_na_important}
